---
title: "Algorithm - Naive Bayes"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = 'C:/Users/oleg/Desktop/Study/year5/semesterA/dataAnalys/HW2/Titanic')
set.seed(123)
```

## Algorithm Used

We choose to use Naive Bayes algorithm like explain in Data Science Intro lesson

For further explaination, see here https://en.wikipedia.org/wiki/Naive_Bayes_classifier>.


## Set directory 

Note that we save a backup of the dataframe as `df.backup`

```{r}s
df <- read.csv("Titanic/train.csv",na.strings = "")
df.bkup <- df
#getwd
```




## Convert Survived column and Pclass column to factors, and extract unwanted columns to dataframe

Note that dont want to take in consideration the following fields:

1. PassengerID

2. Name

3. Ticket

```{r}
df$Survived<- as.factor(df$Survived)
df$Pclass<- as.factor(df$Pclass)
df <- df[,-c(1,4,9)]
```






# Split the data into train and test sets

```{r}
indices <- sample(1:nrow(df),nrow(df)*0.8)
train_df<- df[indices,]
test_df<- df[-indices,]
```






# Train the model based on the train set:

load e1071 library and invoke naiveBayes method

```{r}
#install.packages('e1071')
library(e1071)
nb_model <- naiveBayes(Survived~.,data = df)
```





#Load Dataframe test and save the passenger Ids

```{r}
new_df <-read.csv('Titanic/test.csv',na.strings = "")
ids<- new_df$PassengerId

new_df$Pclass<- as.factor(new_df$Pclass)
new_df<- new_df[,-c(1,3,8)]
```






#Predict target attribute for the test set based on the trained model
```{r}
pred <- predict(nb_model,new_df,na.action = na.pass)
```






#Create result dataframe and write it into csv
```{r}
df_ <- data.frame(PassengerId =ids, Survived = pred)
write.csv(df_, file = "result.csv", row.names = FALSE)
```






